\bf Focusing on Fast Neural Network Inference

### 2018-05-15 wnmt.2018/wnmt.tex
cast

This paper describe the submissions by members of the University of Edinburgh, Adam Mickiewicz University, Tilde and University of Alicante. We submit two systems based on Amun, the fast inference engine for neural machine translation. We partipated

Through efficient implementation and novel enhancements to the algorithms, our fastest submission is by far the fastest in the shared task. By using more complex models and with model distillation, our other submissions combine the inherent speed of our inference engine with better quality translation.

%The team is composed of members from the University of Edinburgh, Adam Mickiewicz University, Microsoft, Tilde, and the Internation Maritime Organization.

@@

Exper

//////////////////////////////////////////////

@@

>>>>

This paper describe the submissions to the efficiency track for GPUs by members of the University of Edinburgh, Adam Mickiewicz University, Tilde and University of Alicante. We focus on efficient implementation of the recurrent deep-learning model as implemented in Amun, the fast inference engine for neural machine translation. We improve the performance with an efficient mini-batching and maxi-batching algorithm. Translation speed was also reduced by fusing the softmax operation with the beam seach algorithm.

@@

\section{Improvements}

We desribe the main enhancements to Amun since the original public in 2016.

\subsection{Batching}

\subsection{Softmax and Beam Search Kernel Fusion}

@@

\subsection{Half-Precision}

/////////////////////////////////////////////////////////////////////////////////////
